04_validation

### 2022-07-22 replication_data/rmd/01_compile_saves_and_align.Rmd
01-04 reproduce

    if(fromscratch){
      icb_crisis_summaries <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")
      #Do a round first based on the file name
      icb_long_crisis_sentence_unique <- icb_long %>% dplyr::select(crisno,  sentence_clean) %>% distinct() %>%  #we have to check two different crises, the one that was reported and the file name
        mutate(crisno= crisno %>% as.numeric()) %>%
        left_join(icb_crisis_summaries %>% dplyr::select(crisno,text) ) %>%
        janitor::clean_names()
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty=NA
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start=NA
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end=NA
      #Ya I'm just going to have to remove parenthetical again, there's no avoiding it
      tic()
        for(i in 1:nrow(icb_long_crisis_sentence_unique)){
          #print(i)
          if(i %% 100 ==0) {print(i)}
          if(!is.na(icb_long_crisis_sentence_unique$sentence_clean[i]) & nchar(icb_long_crisis_sentence_unique$sentence_clean[i])>5){ #there are some broken sentences with few or no characters
            temp1 <- text.alignment::smith_waterman(icb_long_crisis_sentence_unique$sentence_clean[i] , icb_long_crisis_sentence_unique$text[i])
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start[i]=temp1$b$alignment$from
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end[i]=temp1$b$alignment$to
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty[i]=temp1$similarity        
          }
        }
      toc() #878.328 sec elapsed
    icb_long_crisis_sentence_unique %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")
    }
    icb_long_crisis_sentence_unique <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")

>>>>

    if(fromscratch){
      icb_crisis_summaries <- readRDS(here::here("replication_corpus", "data", "out", "icb_corpus_V1.0_May_16_2022.Rds"))

      #Do a round first based on the file name
      icb_long_crisis_sentence_unique <- icb_long %>% dplyr::select(crisno,  sentence_clean) %>% distinct() %>%  #we have to check two different crises, the one that was reported and the file name
        mutate(crisno= crisno %>% as.numeric()) %>%
        left_join(icb_crisis_summaries %>% dplyr::select(crisno,text) ) %>%
        janitor::clean_names()
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty=NA
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start=NA
      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end=NA
      #Ya I'm just going to have to remove parenthetical again, there's no avoiding it
      tic()
        for(i in 1:nrow(icb_long_crisis_sentence_unique)){
          #print(i)
          if(i %% 100 ==0) {print(i)}
          if(!is.na(icb_long_crisis_sentence_unique$sentence_clean[i]) & nchar(icb_long_crisis_sentence_unique$sentence_clean[i])>5){ #there are some broken sentences with few or no characters
            temp1 <- text.alignment::smith_waterman(icb_long_crisis_sentence_unique$sentence_clean[i] , icb_long_crisis_sentence_unique$text[i])
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start[i]=temp1$b$alignment$from
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end[i]=temp1$b$alignment$to
            icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty[i]=temp1$similarity        
          }
        }
      toc() #878.328 sec elapsed
    icb_long_crisis_sentence_unique %>% saveRDS(here::here("replication_corpus", "data", "out", "icb_long_crisis_sentence_unique.Rds"))
    }
    icb_long_crisis_sentence_unique <- readRDS(here::here("replication_corpus", "data", "out", "icb_long_crisis_sentence_unique.Rds"))

### 2022-07-22 replication_data/rmd/04_validation.Rmd
01-04 reproduce

country_flags <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/countries.csv" %>% read_csv(col_names=F)
library(WikidataR)# install.packages("WikidataR","WikidataQueryServiceR")
#https://commons.wikimedia.org/wiki/File:Flag_of_the_United_Nations.svg
UN <- get_item("Q1065")[[1]]$claims$P41

@@

#which(flag_codes1$value_qcode=="Q347")
for(i in 1:nrow(flag_codes1)){
  print(i)
  if(is.na(flag_codes1$wikidata_flag_url[i])){ next }
  destfile_svg <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.svg")
  destfile_png <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.png")

@@

flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
flag_files <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

@@

library(tidyverse)
library(magick) #switching to magick which handles transparency correctly
library(imager); #install.packages("imager")
flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
flag_folder_small <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
#20x16 pixels
file="Q15180"

@@

#![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/cub.png)

>>>>

country_flags <- here::here("replication_data", "in", "countries.csv") %>% read_csv(col_names=F)

library(WikidataR)# install.packages("WikidataR","WikidataQueryServiceR")
#https://commons.wikimedia.org/wiki/File:Flag_of_the_United_Nations.svg
UN <- get_item("Q1065")[[1]]$claims$P41

@@

#which(flag_codes1$value_qcode=="Q347")
for(i in 1:nrow(flag_codes1)){
  print(i)
  if(is.na(flag_codes1$wikidata_flag_url[i])){ next }

  destfile_svg <- glue::glue(here::here("replication_data", "in", "flags", "{flag_codes1$value_qcode[i]}.svg"))
  destfile_png <- glue::glue(here::here("replication_data", "in", "flags", "{flag_codes1$value_qcode[i]}.png"))

@@

flag_folder <- here::here("replication_data", "in", "flags/")
flag_files <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

@@

library(tidyverse)
library(magick) #switching to magick which handles transparency correctly
library(imager); #install.packages("imager")

flag_folder <- here::here("replication_data", "in", "flags/")
flag_folder_small <- here::here("replication_data", "in", "flags_small/")
#20x16 pixels
file="Q15180"

@@

#![](here::here("replication_data", "pnas_draft", "cub.png"))
